Cosmic Microwave Background Power Spectra from Few Bit Timestreams

### 2018-09-20 digitisation.tex
editing

We carry out the same simulations as described in subsection \ref{subsec:method} using the above noise profile and digitisation schemes for maps with $8,000$, $102,400$ and $1,024,000$ hits per pixel. We apply a cosine mask to the revocered maps to minimise boundary effects before using HEALPix to calculate the spherical harmonic coefficients $a\ell m$. We discount modes with $m < \lknee$. The scan strategy of the simulated observations is similar to the SPT's in that smaller values of $m$ correspond to larger angular features along the scan direction \citep{chown2018}. Giving equal weight to all modes would lead to inaccurate power spectra due to the anisotropic nature of the noise. We mask these modes, which is the first order approximation to optimal weighting. The analysis procedure of section \ref{subsec:whitenoise} is used to characterise the additional noise.

@@

The first two terms in the above will lead to even powers of $\mu$, whereas the last two will lead to odd powers of $\mu$. We are now ready to put all pieces together and start by investigating even powers of $\mu$ in equation \ref{eq:dcompleteklsum} that arise from even $k$ and $l$. Under the assumptions made \ref{eq:ijsumpsiflip} reduces to

>>>>

We carry out the same simulations as described in subsection \ref{subsec:method} using the above noise profile and digitisation schemes for maps with $8,000$, $102,400$ and $1,024,000$ hits per pixel. We apply a cosine mask to the revocered maps to minimise boundary effects before using HEALPix to calculate the spherical harmonic coefficients $a\ell m$. We discount modes with $m < \lknee$ before calculating the power spectra. The scan strategy of the simulated observations is similar to the SPT's in that smaller values of $m$ correspond to larger angular features along the scan direction \citep{chown2018}. Giving equal weight to all modes would lead to inaccurate power spectra due to the anisotropic nature of the noise. We mask these modes, which is the first order approximation to optimal weighting. The analysis procedure of section \ref{subsec:whitenoise} is used to characterise the additional noise.

@@

The first two terms in the above will lead to even powers of $\mu$, whereas the last two will lead to odd powers of $\mu$. We are now ready to put all the pieces together and start by investigating even powers of $\mu$ in equation \ref{eq:dcompleteklsum} that arise from even $k$ and $l$. Under the assumptions made \ref{eq:ijsumpsiflip} reduces to
